Problem statement and suggested project outline

### 2011-11-15 background/phd-description1.tex
paper 3
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@36 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\section*{Paper 3: Conditional selectivity in the federated case}

In paper~1, I explored selectivity estimation as a technique for query
optimization. In a federated regime, selectivity estimation is
important because without it, large amounts of data may needlessly be
passed back and forth between different endpoints. However, the
federation engine has no way of estimating the selectivity of the
entire query since it has no record of the structure of the data.

The third paper will explore ways to remedy this situation, e.g. by
compiling statistics that may be exposed in a service description. In
particular, parameterized statistics may be useful.

Finally, techniques developed in paper~2 will be used to evaluate the
efficiency of various techniques.
